The host galaxy of the short GRB~111117A at z = 2.211\thanks{Based on observations collected at the European Southern Observatory, Paranal, Chile, Program ID: 088.A-0051 and 091.D-0904.}

### 2017-05-28 GRB111117A.tex
Add co-authors and add line-breaks to better track changes

\abstract{
Short $\gamma$-ray bursts (sGRBs) and their hosts are notoriously difficult to localize. We here present a spectroscopic observation of the host galaxy of GRB 111117A and measure its redshift to be $z = 2.211$, making it the most distant high-confidence short GRB with a secure redshift measurement. This value supersedes a previously estimated, lower redshift value. Spectroscopic observations along with a wealth of imaging data allow us to place tight constraints on the nature of the host galaxy at an unprecedented distance. 
The rest frame X-ray derived hydrogen column density is high compared to a complete sample of sGRBs and seems to follow the evolution with redshift as traced by the hosts of long GRBs (lGRBs). This could indicate that the part of the sGRB population hosted in late-type galaxies live in similar environments to that of lGRB hosts. 
The host lies in the brighter end of the expected host brightness distribution at $z = 2.211$, and is actively star forming. Using the host as a benchmark for redshift determination, we assess that only 30 per cent of sGRB redshifts should be missed due to host faintness at this redshift. This indicates that we are not missing redshifts for a dominant fraction of the sGRB hosts at this redshift. The redshift of GRB~111117A is evidence against a lognormal delay-time model for sGRBs through the predicted redshift distribution of sGRBs, which is very sensitive to high-z sGRBs.
%From the age of the universe at explosion time, an initial progenitor separation of a$_0 < 3.2 $R$_\odot$ is required for the case of a binary neutron star (NS) system. This puts constraints on the progenitor system evolution up to the time of explosion.
}

@@

There is now mounting evidence that most short-duration gamma-ray bursts (GRBs) come from the merger of neutron stars (NSs), either with another NS, or a black hole, due to their apparent association with kilonovae \citep{Barnes2013a, Tanvir2013b, Yang2015, Jin2016, Rosswog2016}. The absence of associated supernovae in deep searches \citep[e.g.][]{Hjorth2005a,Fox2005,Hjorth2005b} supports this idea and distinguishes the physical origin of sGRBs from their long-duration counterparts.
%\citep[albeit see also][]{Fynbo2006b, Valle2006, Gal-Yam2006}. 
The range of host galaxy types, in some cases apparently absent, and typically more massive 
and on average less actively star-forming than long GRB hosts  \citep{Fong2013b}, as well as their positions within hosts \citep{Fong2013a}, suggest an origin for the progenitors that can be very long-lived, and associated with stellar mass rather than purely star-formation rate \citep{Berger2014}. The bulk of sGRBs have associated galaxies at relatively low redshifts with a median $z\sim0.5$ \citep{Berger2014} and because most redshifts are measured from the hosts, this value is biased towards low $z$.
%This progress on the progenitors of sGRBs has been enabled by the afterglow detection and burst localization by the \emph{Swift} satellite \citep{Gehrels2009a}. The bulk of these localizations have associated galaxies at relatively low redshifts with a median $z\sim0.5$ \citep{Berger2014} and because most redshifts are measured from the hosts, this value is biased towards low $z$.

%So far, the electromagnetic signal from sGRBs are the only means to accurately localize NS mergers and holds the promise for detection of an associated gravitational wave signal \citep{Ghirlanda2016}. From the burst and following afterglow, modeling the properties and mapping the environments additionally allows insights into the phenomenon itself.

@@

In this \emph{Letter} we present the spectrum of the host galaxy of the short GRB 111117A at z=2.211, a significantly higher redshift than the previously estimated redshift based on photometric studies. We present the rest frame burst properties based on this new distance
compared to previous analyses \citep{Margutti2012,Sakamoto2013} and revisit the host properties derived from the new solution to the SED fit. 
%While no optical afterglow was detected, the excellent localization from a detection
%of the X-ray afterglow by the \emph{Chandra X-ray Observatory} also allows
%us to discuss the positioning and environmental properties of this remarkably
%distant short GRB.

@@

%(21000 \AA when the K-band blocking filter is used)
Spectroscopic observations were carried out using the cross-dispersed echelle spectrograph, VLT/X-shooter \citep{Vernet2011}, in four seperate epochs. The burst was followed up 38 hours after the Burst Alert Telescope (BAT) trigger under ESO programme 088.A-0051 (PI: Fynbo) and again later using a different ESO program 091.D-0904 (PI: Hjorth). X-shooter can cover the wavelength range from 3000 \AA~to 24800 \AA~across three spectroscopic arms, simultaneously illuminated through the use of dichroics. The bias-correction, flat-fielding, order tracing, wavelength calibration, rectification, and flux calibration is then carried out using the VLT/X-shooter pipeline version 2.8.4 \citep{Goldoni2006, Modigliani2010} and managed by Reflex \citep{Freudling2013}. Because the spectra are curved across each detector, a rectification algorithm is employed which introduces correlations between neighboring pixels. We select a pixel-scale of 0.2/0.2/0.6 \AA/pix for the UVB/VIS/NIR arm to minimize the degree of correlation while conserving the maximal resolution. The observations are combined and extracted using scripts described in Selsing et al. 2017 (in prep.) and available online\footnote{\url{https://github.com/jselsing/XSGRB_reduction_scripts}}. The signal-to-noise of the continuum in the near-infrared arm is too low to use the optimal extraction algorithm \citep{Horne1986} and therefore the extraction is carried out with a simple aperture.
An overview of the spectroscopic observations is given in Tab. \ref{tab:spec_overview}, and the position of the slit on the target is shown in Fig. \ref{fig:spec_setup}.

@@

%The total extent of the lines in velocity space is $\sim$ 450 km/s. The line profiles shows an asymmetric "double-horned" profile, indicating that we are seeing a galaxy with a large degree of coherent rotational motion relative to the line-of-sight. If we assume that we are viewing a spiral galaxy exactly edge-on, this is a measure of the rotational velocity of the gas. If we assume that the spectral resolution and the turbulent width of the lines are negligible compared to the rotational velocity, we can based on the projected size of the source and the width of the lines, put a constraint on the dynamical mass of the galaxy. Based on the physical scale from extent and the velocity with, we infer M$_\text{dyn} \gtrsim 10^{10.8}$ M$_\odot$. Because we are viewing the host at an angle, this value is an upper limit, which should be divided by $\sin(i)$, where $i$ is the inclination relative to edge-on.

Using the integrated flux of \ha, we can infer the SFR \citep{Kennicutt1998, Moustakas2006}. From the SED-fit, see Sect. \ref{SED}, and the detection of \lya, the host is constrained to contain very little or no dust which is also confirmed by the shape of the spectral continuum, which is why we do not apply a dust-correction. Because of the redshift, \ha~falls on the far end of the NIR-arm where the night sky is very bright and additionally, several bright sky-lines intersect the line, making an accurate estimate of the \ha-flux difficult. %Because of the challenging measurement, two approaches are employed. First, 
A limit on the SFR is obtained by integrating the part of \ha~free of contamination and conservatively correcting for the missing fraction by assessing the fraction integrated. Converting to a \citet{Chabrier2003} initial mass function using \citet{Madau2014} we get a limit of SFR > 7 M$_\odot$ yr$^{-1}$. %Secondly, based on the width of \oiii, an aperture covering the line is integrated over, where synthetic sky lines \citep{Noll2012, Jones2013} have been masked and interpolated over. From the integrated \ha-line, we estimate SFR = $18 \pm 3$ M$_\odot$ yr$^{-1}$.

@@

%A measure of the optical-to-X-ray flux ratio is parametrized in terms of the "darkness"-parameter $\beta_{OX}$\citep{Jakobsson2004}. Using the optical afterglow limits\citep{Cucchiara2011, Cenko2011}, the X-ray lightcurve can be interpolated and evaluated at the time of the non-detection. We find $\beta_{OX} < 0.79$, consistent with what was reported in \citet{Sakamoto2013}.

%Because the projected distance does not change much between redshift 1.3 and 2.1, all conclusions of \citet{Margutti2012} and \citet{Sakamoto2013} relating to host offset are unaffected.

@@

The multi-color spectral energy distribution (SED) is then fit by \citet{Bruzual2003} stellar population synthesis models based on a \citet{Chabrier2003} initial mass function in \emph{LePhare} \citep{Ilbert2006}, where the redshift is fixed to the spectroscopic value of $z=2.211$. The best model is obtained with an unreddened galaxy template, and returns physical parameters of luminosity ($M_B=-22.0\pm0.1$\,mag), stellar mass ($\log(M_{\star}/M_\odot) = 9.9\pm0.2$), single stellar population age ($\tau = 0.5_{-0.25}^{+0.5}$ Gyr) and star-formation rate ($SFR_{\mathrm{SED}}=11_{-4}^{+9} M_\odot\,\mathrm{yr}^{-1}$). %We show the SED fit in Fig. \ref{fig:SED}.

@@

%From the clear host association, GRB~111117A does not belong to the hostless class of GRBs \citep{Berger2010a} and because the host exhibits clear emission lines indicative of a population of relatively young stars, 
As the majority of short GRBs \citep{Fong2013b}, the host of GRB~111117A is a late-type galaxy and is entirely consistent in terms of stellar mass and stellar age with the general population of short GRB hosts($\left\langle M _* \right\rangle = 10^{10.1} M_{\odot}$ and $\left\langle \tau _* \right\rangle = 0.3 $ Gyr) \citet{Leibler2010}. The SFR, on the other hand, is $\sim$1 order of magnitude higher than the typical SFR for short GRB hosts galaxies \citep{Berger2014} and more similar to the SFRs found in the hosts of long GRBs at a corresponding redshift \citep{Kruhler2015}. Only two hosts in the sample of short GRBs compiled in \citet{Berger2014} have a more vigorous star formation, meaning that it is in the very upper end of the star formation distribution, while not a complete outlier. This is likely a selection effect, because a less star-forming galaxy would exhibit weaker emission lines, thus making the redshift harder to determine. Being a late-type host, both the stellar mass and sSFR are entirely consistent with the expected host of sGRBs\citep{Behroozi2014}.
That we detect \lya~is consistent with the SED-inferred absence of dust, despite the moderate stellar age and the high X-ray derived hydrogen column density which would suggest the opposite. The centroid of the Ly$\alpha$ emission is found to be redshifted by $\sim$ 220 km s$^{-1}$ with respect to systemic, which is similar to what is found for long GRB hosts \citep{Milvang-Jensen2012a} where the outflow is attributed to star formation.

@@

At $z = 2.211$, the age of the universe is 2.97 Gyr. If the progenitor systems of sGRBs are the merger of two neutron stars, this sets a hard upper limit to the coalescence timescale for such a system. In the absence of other mechanisms, the timescale of the orbital decay of the system is set by the energy loss due to gravitational waves, which in turn is set by the mass of constituent compact objects and the separation of the two \citep{Postnov2014}. If we assume that the formation timescale of the first galaxies is short compared to the time since the big bang \citep{Richard2011} and if we assume a mass of 1.4 M$_\odot$ for each of the neutron stars at the time of system formation, this places a limit on the initial separation of the two neutron stars of a$_0 < 3.2 $R$_\odot$, where a$_0$ is the initial separation. 
Assuming our measured age of the stellar population ($\tau = 0.5$ Gyr) as a limit for the orbital decay time we can put a tighter constraint of a$_0 < 2.1 $R$_\odot$. However, this does not account for the possibility there could be an underlying stellar population of older stars from a previous star-formation epoch, which is why we consider a$_0 < 3.2 $R$_\odot$ as a hard upper limit. The delay time between formation and explosion is well accomodated by the models of \citet{Belczynski2006}, although the longest formation channels are excluded. This is especially true given the late type nature of the host \citep{OShaughnessy2008}.

>>>>

\abstract{
Short $\gamma$-ray bursts (sGRBs) and their hosts are notoriously difficult to
localize. We here present a spectroscopic observation of the host galaxy of GRB
111117A and measure its redshift to be $z = 2.211$, making it the most distant
high-confidence short GRB with a secure redshift measurement. This value
supersedes a previously estimated, lower redshift value. Spectroscopic
observations along with a wealth of imaging data allow us to place tight
constraints on the nature of the host galaxy at an unprecedented distance.

The rest frame X-ray derived hydrogen column density is high compared to a
complete sample of sGRBs and seems to follow the evolution with redshift as
traced by the hosts of long GRBs (lGRBs). This could indicate that the part of
the sGRB population hosted in late-type galaxies live in similar environments to
that of lGRB hosts.

The host lies in the brighter end of the expected host brightness distribution
at $z = 2.211$, and is actively star forming. Using the host as a benchmark for
redshift determination, we assess that only 30 per cent of sGRB redshifts should
be missed due to host faintness at this redshift. This indicates that we are not
missing redshifts for a dominant fraction of the sGRB hosts at this redshift.
The redshift of GRB~111117A is evidence against a lognormal delay-time model for
sGRBs through the predicted redshift distribution of sGRBs, which is very
sensitive to high-z sGRBs.

From the age of the universe at explosion time, an initial progenitor separation
of a$_0 < 3.2 $R$_\odot$ is required for the case of a binary neutron star (NS)
system. This puts constraints on the progenitor system evolution up to the time
of explosion.
}

@@

There is now mounting evidence that most short-duration gamma-ray bursts (GRBs)
come from the merger of neutron stars (NSs), either with another NS, or a black
hole, due to their apparent association with kilonovae \citep{Barnes2013a,
	Tanvir2013b, Yang2015, Jin2016, Rosswog2016}. The absence of associated
supernovae in deep searches \citep[e.g.][]{Hjorth2005a,Fox2005,Hjorth2005b}
supports this idea and distinguishes the physical origin of sGRBs from their
long-duration counterparts. %\citep[albeit see also][]{Fynbo2006b, Valle2006,
% Gal-Yam2006}.
The range of host galaxy types, in some cases apparently absent, and typically
more massive and on average less actively star-forming than long GRB hosts 
\citep{Fong2013b}, as well as their positions within hosts \citep{Fong2013a},
suggest an origin for the progenitors that can be very long-lived, and
associated with stellar mass rather than purely star-formation rate
\citep{Berger2014}. The bulk of sGRBs have associated galaxies at relatively low
redshifts with a median $z\sim0.5$ \citep{Berger2014} and because most redshifts
are measured from the hosts, this value is biased towards low $z$.

%This progress on the progenitors of sGRBs has been enabled by the afterglow
% detection and burst localization by the \emph{Swift} satellite
% \citep{Gehrels2009a}. The bulk of these localizations have associated galaxies
% at relatively low redshifts with a median $z\sim0.5$ \citep{Berger2014} and
% because most redshifts are measured from the hosts, this value is biased
% towards low $z$.

%So far, the electromagnetic signal from sGRBs are the only means to accurately
% localize NS mergers and holds the promise for detection of an associated
% gravitational wave signal \citep{Ghirlanda2016}. From the burst and following
% afterglow, modeling the properties and mapping the environments additionally
% allows insights into the phenomenon itself.

@@

In this \emph{Letter} we present the spectrum of the host galaxy of the short
GRB 111117A at z=2.211, a significantly higher redshift than the previously
estimated redshift based on photometric studies. We present the rest frame burst
properties based on this new distance compared to previous analyses
\citep{Margutti2012,Sakamoto2013} and revisit the host properties derived from
the new solution to the SED fit. %While no optical afterglow was detected, the
% excellent localization from a detection
%of the X-ray afterglow by the \emph{Chandra X-ray Observatory} also allows
%us to discuss the positioning and environmental properties of this remarkably
%distant short GRB.

@@

Spectroscopic observations were carried out using the cross-dispersed echelle
spectrograph, VLT/X-shooter \citep{Vernet2011}, in four seperate epochs. The
burst was followed up 38 hours after the Burst Alert Telescope (BAT) trigger
under ESO programme 088.A-0051 (PI: Fynbo) and again later using a different ESO
program 091.D-0904 (PI: Hjorth). X-shooter can cover the wavelength range from
3000 \AA~to 24800 \AA~(21000 \AA~when the K-band blocking filter is used)~across
three spectroscopic arms, simultaneously illuminated through the use of
dichroics. The bias-correction, flat-fielding, order tracing, wavelength
calibration, rectification, and flux calibration is then carried out using the
VLT/X-shooter pipeline version 2.8.4 \citep{Modigliani2010}. 
%Because the spectra are curved across each detector, a rectification algorithm
%is employed which introduces correlations between neighboring pixels. We select
%a pixel-scale of 0.2/0.2/0.6 \AA/pix for the UVB/VIS/NIR arm to minimize the
%degree of correlation while conserving the maximal resolution.
The observations are combined and extracted using scripts described in Selsing
et al. 2017 (in prep.) and available
online\footnote{\url{https://github.com/jselsing/XSGRB_reduction_scripts}}. The
signal-to-noise of the continuum in the near-infrared arm is too low to use the
optimal extraction algorithm \citep{Horne1986} and therefore the extraction is
carried out with a simple aperture.

An overview of the spectroscopic observations is given in Tab. \ref{tab:spec_overview}, and the position of the slit on the target is shown in Fig. \ref{fig:spec_setup}.

@@

%The total extent of the lines in velocity space is $\sim$ 450 km/s. The line
% profiles shows an asymmetric "double-horned" profile, indicating that we are
% seeing a galaxy with a large degree of coherent rotational motion relative to
% the line-of-sight. If we assume that we are viewing a spiral galaxy exactly
% edge-on, this is a measure of the rotational velocity of the gas. If we assume
% that the spectral resolution and the turbulent width of the lines are
% negligible compared to the rotational velocity, we can based on the projected
% size of the source and the width of the lines, put a constraint on the
% dynamical mass of the galaxy. Based on the physical scale from extent and the
% velocity with, we infer M$_\text{dyn} \gtrsim 10^{10.8}$ M$_\odot$. Because we
% are viewing the host at an angle, this value is an upper limit, which should
% be divided by $\sin(i)$, where $i$ is the inclination relative to edge-on.

Using the integrated flux of \ha, we can infer the SFR \citep{Kennicutt1998}.
From the SED-fit, see Sect. \ref{SED}, and the detection of \lya, the host is
constrained to contain very little or no dust which is also confirmed by the
shape of the spectral continuum, which is why we do not apply a dust-correction.
Because of the redshift, \ha~falls on the far end of the NIR-arm where the night
sky is very bright and additionally, several bright sky-lines intersect the
line, making an accurate estimate of the \ha-flux difficult. A limit on the SFR
is obtained by integrating the part of \ha~free of contamination and
conservatively correcting for the missing fraction by assessing the fraction
integrated. Converting to a \citet{Chabrier2003} initial mass function using
\citet{Madau2014} we get a limit of SFR > 7 M$_\odot$ yr$^{-1}$.

%Secondly, based on the width of \oiii, an aperture covering the line
% is integrated over, where synthetic sky lines \citep{Noll2012, Jones2013} have
% been masked and interpolated over. From the integrated \ha-line, we estimate
% SFR = $18 \pm 3$ M$_\odot$ yr$^{-1}$.

@@

%A measure of the optical-to-X-ray flux ratio is parametrized in terms of the
% "darkness"-parameter $\beta_{OX}$\citep{Jakobsson2004}. Using the optical
% afterglow limits\citep{Cucchiara2011, Cenko2011}, the X-ray lightcurve can be
% interpolated and evaluated at the time of the non-detection. We find
% $\beta_{OX} < 0.79$, consistent with what was reported in \citet{Sakamoto2013}.

%Because the projected distance does not change much between redshift 1.3 and
% 2.1, all conclusions of \citet{Margutti2012} and \citet{Sakamoto2013} relating
% to host offset are unaffected.

@@

The multi-color spectral energy distribution (SED) is then fit by
\citet{Bruzual2003} stellar population synthesis models based on a
\citet{Chabrier2003} initial mass function in \emph{LePhare} \citep{Ilbert2006},
where the redshift is fixed to the spectroscopic value of $z=2.211$. The best
model is obtained with an unreddened galaxy template, and returns physical
parameters of luminosity ($M_B=-22.0\pm0.1$\,mag), stellar mass
($\log(M_{\star}/M_\odot) = 9.9\pm0.2$), single stellar population age ($\tau =
0.5_{-0.25}^{+0.5}$ Gyr) and star-formation rate
($SFR_{\mathrm{SED}}=11_{-4}^{+9} M_\odot\,\mathrm{yr}^{-1}$). %We show the SED
% fit in Fig. \ref{fig:SED}.

@@

%From the clear host association, GRB~111117A does not belong to the hostless class of GRBs \citep{Berger2010a} and because the host exhibits clear emission lines indicative of a population of relatively young stars, 
As the majority of short GRBs \citep{Fong2013b}, the host of GRB~111117A is a
late-type galaxy and is entirely consistent in terms of stellar mass and stellar
age with the general population of short GRB hosts($\left\langle M _*
\right\rangle = 10^{10.1} M_{\odot}$ and $\left\langle \tau _* \right\rangle =
0.3 $ Gyr) \citet{Leibler2010}. The SFR, on the other hand, is $\sim$1 order of
magnitude higher than the typical SFR for short GRB hosts galaxies
\citep{Berger2014} and more similar to the SFRs found in the hosts of long GRBs
at a corresponding redshift \citep{Kruhler2015}. Only two hosts in the sample of
short GRBs compiled in \citet{Berger2014} have a more vigorous star formation,
meaning that it is in the very upper end of the star formation distribution,
while not a complete outlier. This is likely a selection effect, because a less
star-forming galaxy would exhibit weaker emission lines, thus making the
redshift harder to determine. Being a late-type host, both the stellar mass and
sSFR are entirely consistent with the expected host of
sGRBs\citep{Behroozi2014}.

That we detect \lya~is consistent with the SED-inferred absence of dust, despite
the moderate stellar age and the high X-ray derived hydrogen column density
which would suggest the opposite. The centroid of the Ly$\alpha$ emission is
found to be redshifted by $\sim$ 220 km s$^{-1}$ with respect to systemic, which
is similar to what is found for long GRB hosts \citep{Milvang-Jensen2012a} where
the outflow is attributed to star formation.

@@

At $z = 2.211$, the age of the universe is 2.97 Gyr. If the progenitor systems
of sGRBs are the merger of two neutron stars, this sets a hard upper limit to
the coalescence timescale for such a system. In the absence of other mechanisms,
the timescale of the orbital decay of the system is set by the energy loss due
to gravitational waves, which in turn is set by the mass of constituent compact
objects and the separation of the two \citep{Postnov2014}. If we assume that the
formation timescale of the first galaxies is short compared to the time since
the big bang \citep{Richard2011} and if we assume a mass of 1.4 M$_\odot$ for
each of the neutron stars at the time of system formation, this places a limit
on the initial separation of the two neutron stars of a$_0 < 3.2 $R$_\odot$,
where a$_0$ is the initial separation.

Assuming our measured age of the stellar population ($\tau = 0.5$ Gyr) as a
limit for the orbital decay time we can put a tighter constraint of a$_0 < 2.1
$R$_\odot$. However, this does not account for the possibility there could be an
underlying stellar population of older stars from a previous star-formation
epoch, which is why we consider a$_0 < 3.2 $R$_\odot$ as a hard upper limit. The
delay time between formation and explosion is well accomodated by the models of
\citet{Belczynski2006}, although the longest formation channels are excluded.
This is especially true given the late type nature of the host
\citep{OShaughnessy2008}.

### 2017-05-28 authorlist.tex
Add co-authors and add line-breaks to better track changes

\author{J.~Selsing\inst{1}
\and T. Kr\"{u}hler\inst{2}
\and D.~Malesani\inst{1,3}
\and P. D'Avanzo\inst{4}
\and J.~Palmerio\inst{5}
\and S.~D.~Vergani\inst{6}
\and J.~Japelj\inst{6}
\and B.~Milvang-Jensen\inst{1}
\and D.~Watson\inst{1}
\and P.~Jakobsson\inst{7}
%
\and Z. Cano\inst{8}
\and J.~P.~U.~Fynbo\inst{1}
\and A. Gomboc\inst{9}
\and K.~E.~Heintz\inst{7,1}
\and M. Sparre\inst{1,10}
\and XSGRB collaboration
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
%2
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
%3
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, DK-2800 Lyngby, Denmark
%4
\and INAF - Osservatorio Astronomico di Brera, via E. Bianchi 46, I-23807, Merate (LC), Italy
%5
\and Sorbonne Universités, UPMC Univ. Paris 6 et CNRS, UMR 7095, Institut d’Astrophysique de Paris, 98 bis bd Arago, 75014 Paris, France
%6
\and GEPI, Observatoire de Paris, PSL Research University, CNRS, Univ. Paris Diderot, Sorbonne Paris Cité, 5 Place Jules Janssen, 92195 Meudon, France
%7
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107 Reykjav\'ik, Iceland
%8
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain.
%9
\and University of Nova Gorica, Vipavska 13, 5000 Nova Gorica, Slovenia.
%10
\and Heidelberger Institut f{\"u}r Theoretische Studien, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany 
%\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
}

>>>>

\author{J.~Selsing\inst{1}
\and T.~Kr\"{u}hler\inst{2}
\and D.~Malesani\inst{1,3}
\and P.~D'Avanzo\inst{4}
\and J.~Palmerio\inst{5}
\and S.~D.~Vergani\inst{6}
\and J.~Japelj\inst{7}
\and B.~Milvang-Jensen\inst{1}
\and D.~Watson\inst{1}
\and P.~Jakobsson\inst{8}
%
\and Z.~Cano\inst{9}
%\and L.~B.~Christensen\inst{1}
\and V.~D'Elia\inst{10}
\and A.~de~Ugarte~Postigo\inst{9, 1}
\and J.~P.~U.~Fynbo\inst{1}
\and A.~Gomboc\inst{11}
\and K.~E.~Heintz\inst{8,1}
\and A.~J.~Levan \inst{12}
\and M.~Sparre\inst{1,13}
\and N.~R.~Tanvir\inst{14}
\and C.~C.~Th\"one\inst{9}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
%2
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
%3
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, DK-2800 Lyngby, Denmark
%4
\and INAF - Osservatorio Astronomico di Brera, via E. Bianchi 46, I-23807, Merate (LC), Italy
%5
\and Sorbonne Universités, UPMC Univ. Paris 6 et CNRS, UMR 7095, Institut d’Astrophysique de Paris, 98 bis bd Arago, 75014 Paris, France
%6
\and GEPI, Observatoire de Paris, PSL Research University, CNRS, Univ. Paris Diderot, Sorbonne Paris Cité, 5 Place Jules Janssen, 92195 Meudon, France
%7
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands
%8
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107 Reykjav\'ik, Iceland
%9
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain.
%10
\and INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy;
ASI-Science Data Centre, Via del Politecnico snc, I-00133 Rome, Italy
%11
\and University of Nova Gorica, Vipavska 13, 5000 Nova Gorica, Slovenia.
%12
\and Department of Physics, University of Warwick, Coventry CV4 7AL, UK
%13
\and Heidelberger Institut f{\"u}r Theoretische Studien, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany 
%14
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, UK
%\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
}
